---
title: ""
format: 
  html:
    theme: journal
    css: custom2.css
editor: visual
knitr:
  opts_chunk: 
    echo: false
    message: false
    warning: false
---

```{r}
#| include: false
#| cache: false
googlesheets4::gs4_deauth()
cv_url <- "https://docs.google.com/spreadsheets/d/1d9JTogexP-g_WCEqoQV3H2ZHHrenUWqRmmN4l0JEiRA/edit?usp=sharing"
cv <- googlesheets4::read_sheet(cv_url)
```

<!-- Sidebar -->

::: columns
::: {.column .aside width="25%"}
<center><a href='' target='_blank'> ![](https://avatars.githubusercontent.com/u/89318961?s=400&u=10abb055dea5b8f63b35145cc3aa13098b4210ba&v=4){width="80%" style="border-radius: 50%;"}</center>

</a>

### Contact

<center><span style="font-size: 1.5em;"> <a href='https://www.researchgate.net/profile/Laila-Viana-Almeida' target='_blank'><i class="fa-brands fa-researchgate"></i></a> <a href='mailto:lailavalmeida@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://www.linkedin.com/in/lailaviana/' target='_blank'><i class="fa-brands fa-linkedin"></i></a> <a href='https://github.com/lailaviana' target='_blank'><i class="fa-brands fa-github"></i></a></center>

</span>

Hi, my name is Laila Viana and I'm a biologist working with TryTrips since 2013. I have experience in molecular biology and bioinformatics. I am currently working with DNA and RNA sequencing analysis, trying to understand what makes *T. cruzi* capable of invading different cell types.

### Languages

**Portuguese:** Native <br> **English:** Advanced <br>

### Awards

<i class="far fa-star"></i> Academic Relevance (UFMG) - 2014/2015

<i class="far fa-star"></i> Zigman Brener Award (SBPz) - 2015

<i class="far fa-star"></i> Walter Colli Award (SBPz) - 2016/2018 (Co-author)

<i class="far fa-star"></i> Honorable Mention (X-meeting) - 2016 (Co-author)

### Programming skills

<i class="fas fa-laptop"></i> Bash <br><i class="fab fa-r-project"></i> R <br> <i class="fa fa-area-chart" aria-hidden="true"></i> tidyverse <br> <i class="fab fa-markdown"></i> RMarkdown / Quarto <br> <i class="fas fa-code-branch"></i> Git <br> <i class="fab fa-github"></i> GitHub
:::

::: {.column width="5%"}
:::

::: {.column width="70%"}
<!-- Functions -->

```{r}
col_br <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0(col, ""),
      ""
    )
}
col_br_loc <- function(col){
    dplyr::if_else(
      !is.na(col) & col != "N/A|NA", 
      paste0('<br><i class="fa-solid fa-location-dot"></i> ', col),
      ""
    )
}
create_section <- function(cv_data, section_name){
  cv_data |>
    dplyr::mutate(in_resume = as.character(in_resume),
                  end = tidyr::replace_na(end, 9999),
                  loc = dplyr::if_else(loc == "Online", NA_character_, loc)) |>
    dplyr::filter(in_resume %in% c("TRUE", "VERDADEIRO"), section == section_name) |>
    dplyr::select(section:description_1) |>
    dplyr::arrange(desc(end), desc(start)) |>
    dplyr::mutate(
      date =
        dplyr::case_when(
          end == 9999 ~ glue::glue("Current <br> | <br> {start}"),
          end != start ~ glue::glue("{end} <br> | <br> {start}"),
          end == start ~ glue::glue("{end}"),
          TRUE ~ ""
        ) ,
      .before = everything()
    ) |>
    dplyr::mutate(
      main_text =
        glue::glue(
          "**{title}** <br> {col_br(institution)} {col_br(description_1)} {col_br_loc(loc)}"),
      .after = date
    ) |>
    dplyr::select(-c(start, end, section, title, institution, loc, description_1)) |>
    gt::gt() |>
    gt::fmt_markdown(columns = c(date, main_text)) |> 
    gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) |> 
    gt::cols_align(align = "left", columns = main_text)
}
```

<!-- Main content -->

# Laila Viana de Almeida

## <i class="fa-solid fa-graduation-cap"></i> Education

```{r}
create_section(cv, "education")
```

## <i class="fa-solid fa-flask-vial"></i> Lab Skills

```{r}
create_section(cv, "lab_skills")
```

## <i class="fa-solid fa-newspaper"></i> Publications

```{r}
create_section(cv, "publications_journals")
```

## <i class="fa-solid fa-chalkboard-user"></i> Short Courses

```{r}
create_section(cv, "short_courses")
```
:::
:::

<!-- footer -->

<p class="footer">

Resume made with [Quarto](https://quarto.org/). Last updated on `r format.Date(Sys.Date(), "%b %d, %Y")`. <br>License: [CC BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/).

</p>

```{=html}
<script src="https://kit.fontawesome.com/1bb720cc6f.js" crossorigin="anonymous"></script>
```
